Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-02-18 Paper/paper.tex
minor improvements

	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.

@@

	\subsubsection{Conclusions}
	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience not only for blind but all players and ways to improve existing accessibility features and tools (RQ3) by using AI.

	\subsubsection{Further Work}
	There are still open challenges such as the full integration of echolocation techniques as well as additional research in using AI in testing phases and audio description generation.
	Future studies should focus on the echolocation technology for gaming, exploring AI in creating dynamic audio descriptions and identifying missing accessibility features, and developing more haptic feedback systems.

>>>>

	In the past, video games were not designed with accessibility in mind, which resulted in bad gaming experience for people with disabilities. 
	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.

@@

	\subsection{Conclusion}
	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience not only for blind but all players and ways to improve existing accessibility features and tools (RQ3) by using AI.

	\subsection{Further Work}
	There are still open challenges such as the full integration of echolocation techniques as well as additional research in using AI in testing phases and audio description generation.
	Future studies should focus on the echolocation technology for gaming, exploring AI in creating dynamic audio descriptions and identifying missing accessibility features, and developing more haptic feedback systems.
